Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-02-24 tpe_edreview_rebuttal.txt

> between Eq. (1) and Eq. (3) denote the same quantity.  Why use
> different symbols?
>

corrected, now using $\ell$ consistently for proper length.

> 8.  Suggestion: In the line above Eq. (3), if $w >> 0$ then one does
> not need absolute value bars in $|w|<< 1$.
> 
> 9.  Question.  2nd line below Eq. (4), why are radial strings
> "arbitrarily" longer than flat space would imply?  It appears the
> difference is a matter of calculation (or measurement), not arbitrary.
> Please explain this choice of words.
> 
> 10. Suggestion.  Line below Eq. (5), I think the word "dashes" should
> be "primes".  This is a dash: --- and this is a prime: ', at least in
> usage with which I am familiar.
> 
> 11.  The paragraph below Eq. (6) is puzzling.  Here the path of the
> tight string is being compared to an "equatorial null geodesic," which
> I take to mean the path of a light beam moving along the equator.  If
> we are considering a light beam, then shouldn't a term with $t$ in it
> appear somewhere?  The puzzlement continues given the statement that
> "light, being sensitive to the time component of the metric" whereas
> the equations discussed in this paragraph say nothing (that I can see)
> about the time component of the metric.  The proper time interval
> would be zero, but the coordinate time interval $dt$ would, I think,
> be nonzero.  What am I missing?
> 
> 12.  In the passage below Eq. (6), I am having trouble making the
> connection between $r''(\phi)=r-3M + 2(r')^2/r$ and the claim that the
> solution is $r=r_0\sec(\phi-\phi_0)$.  What trig identity am I
> missing?
> 
> 13.  Can the author explain more fully what is meant by a "tangential
> null geodesic" (several lines after Eq. 6)?  That terminology makes it
> sound like the r-coordinate does not change, whence $r'$ would be
> zero, but that appears to not be the case.  In this section, if $r'$
> is small I see where the approximation $r''=r-2M$ comes from, but I am
> having trouble seeing where $r''-r-3M$ arises for the alleged
> tangential null geodesics.  What am I not seeing?
> 
> I will have to take the author's word for the numerical results.
> 
> This is an interesting paper.  I congratulate the author for thinking
> of such an intriguing application of the Schwarzschild metric.
> However, in this reviewer's opinion, before the paper can be well
> fitted to its announced audience ("an undergraduate homework problem")
> some points need to be clarified.

### 2021-02-24 string_physics_educator_revision3.tex
fixes #40

\documentclass{ws-tpe}
\usepackage{multicol}
\usepackage{units}
\usepackage[superscript]{cite}
\begin{document}

@@

\noindent Here I consider the spatial component~$ds^2=
dr^2/\left(1-2M/r\right) + r^2d\phi^2$, confined to equatorial
points~($\theta=\pi/2$); we understand~$r\geqslant 2M$ throughout.  A
circular string at constant~$r$ will, trivially, have proper
length~$2\pi r$.  Considering first the radial component we may
calculate the proper length $L\left(r_1,r_2\right)$ of a string
stretching from~$r=r_1\geqslant 2M$ to~$r_2\geqslant r_1$ at constant
$\theta,\phi$:

>>>>

\documentclass{ws-tpe}
\usepackage{multicol}
\usepackage{units}
\usepackage{xcolor}
\usepackage[superscript]{cite}
\begin{document}

@@

\noindent Here I consider the spatial component~$ds^2=
dr^2/\left(1-2M/r\right) + r^2d\phi^2$, confined to equatorial
points~($\theta=\pi/2$); we understand~$r\geqslant 2M$ throughout.  A
circular string at constant~$r$ will, trivially, have proper
length~$2\pi r$.  Considering first the radial component we may
calculate the proper length $\ell\left(r_1,r_2\right)$ of a string
stretching from~$r=r_1\geqslant 2M$ to~$r_2\geqslant r_1$ at constant
$\theta,\phi$:
